Global Life Expectancy: Unraveling Health and Economic Determinants (2015-2020)\thanks{Code and data are available at: \url{https://github.com/wendyhuan/lifeexpectancy}.}

### 2024-12-04 paper/paper.tex
initial

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

To make such table, we first select and rename key variables from raw
data to focus on relevant information. To make the subsequent analysis
easier, we then convert variables to the proper data types and eliminate
the rows that have missing data values. To keep things neat, we organize
the decimal for every piece of numerical data and drop the percentage
symbol. The income group column and the region column was not given in
the raw dataset. We created a mapping over country name to four income
group according to the index given by World Bank Income Group and save
the data under ``Income\_Group''. We as well made a mapping to the
countries according to its continent and saved as ``Region''. We again
merge the table, removing repeated columns and rows. For easier
visualization, we created four tables, which are grouped by life
expectancy at age 60, life expectancy at birth, life expectancy at birth
of Male and life expectancy at birth of Female.

shows the average of life expectancy under male, female, 6 different
regions and 4 income groups.

@@

@@

Figure~\ref{fig-expectancy} visualizes the distribution of life
expectancy from 2015 to 2020 as percentages, combining a histogram and a
density plot. A large concentration of observations is observed range of
0\% to 25\%, reflecting a significant proportion of countries with lower
life expectancy relative to others in the dataset. Another visible
concentration is around 75\% to 100\%, indicating a group of countries
with relatively high life expectancy. The blue density curve overlays
the histogram, providing a smoothed representation of the distribution.
Peaks in the curve correspond to high frequency within the histogram.
The density plot emphasized the bimodal nature of the distribution with
two distinct peaks: one around 12 as low life expectancy percentages;
another peak around 87as high life expectancy percentage.

@@

\caption{\label{fig-expectancy}This histogram shows the distribution of
the percentage of life expectancy. With a huge gap between 25 and 50, we
could indicate that most of the countries has a life expectancy of.
There exist large data with low life expectancy less than 25 years.}

@@

\begin{table}
\centering
\caption{Summary Statistics of Life Expectancy}
\centering
\begin{tabular}[t]{c|c|c|c|c|c}
\hline
Mean & Median & Max & Standard Deviation & Variance & N\\
\hline
45.9 & 37.7 & 87.4 & 26.9 & 724.2 & 6624\\
\hline
\end{tabular}
\end{table}

@@

\begin{align} 
y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_1 \text{Region}_i + \beta_2 \text{Gender}_i + \beta_3 \text{Income_Group}_i \\
\alpha &\sim \text{Normal}(0, 2.5) \\
\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 2.5) \\
\sigma &\sim \text{Exponential}(1)
\end{align}

@@

RMSE measures the square root of the average squared differences between
the predicted and observed values. In the context of this model, RMSE
quantifies how closely the predicted life expectancy values align with
the actual observed values. Lower RMSE values indicate better model
performance, suggesting that the model's predictions are close to the
true values. The generalizability is checked by comparing rmse\_test and
rmse\_train. Seeing the test RMSE is slightly lower than the training
RMSE, the model generalizes well.

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#model\_developed \textless{}{-}}
  \CommentTok{\#readRDS(file = "\textasciitilde{}/lifeexpectancy/models/ledata\_normal\_model.rds")}

\CommentTok{\# Split the dataset into training and testing sets (80\% train, 20\% test)}
\CommentTok{\#set.seed(123)  \# Setting seed for reproducibility}
\CommentTok{\#train\_index \textless{}{-} createDataPartition(leab$\textasciigrave{}Life Expectancy\textasciigrave{}, p = 0.8, list = FALSE)}

\CommentTok{\#train\_data \textless{}{-} leab[train\_index, ]}
\CommentTok{\#test\_data \textless{}{-} leab[{-}train\_index, ]}

\CommentTok{\# Predict life expectancy using the test data}
\CommentTok{\#predictions \textless{}{-} predict(ledata\_normal\_model, newdata = test\_data)}
\end{Highlighting}
\end{Shaded}

@@

@@

Our results are summarized in Table~\ref{tbl-modelresults}. We are
primarily interest in the

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{rotating}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

To make such table, we first select and rename key variables from raw
data to focus on relevant information. To make the subsequent analysis
easier, we then convert variables to the proper data types and eliminate
the rows that have missing data values. To keep things neat, we organize
the decimal for every piece of numerical data and drop the percentage
symbol. The income group column and the region column was not given in
the raw dataset. We created a mapping over country name to four income
group according to the index given by World Bank Income Group and save
the data under ``Income\_Group''. We as well made a mapping to the
countries according to its continent and saved as ``Region''. We again
merge the table, removing repeated columns and rows. For easier
visualization, we created four tables, which are grouped by life
expectancy at age 60, life expectancy at birth, life expectancy at birth
of Male and life expectancy at birth of Female. For easier summary and
convenience for graph drawing, we calculate the average of life
expectancy of each country under 6 years. Also, we calculate the average
of 6 years life expectancy according to the other 4 income groups and
different gender by mutate according to the different factors. We then
merge the columns of each table into a summary table for easy looking.

\textbf{?@fig-sum\_sta} shows the average of life expectancy under male,
female, 6 different regions and 4 income groups. Life expectancy
according to different countries have attached and be found in data
cleaning full data in Section~\ref{sec-appendix}.

@@

\begin{table}

\caption{\label{tbl-sum_sta}}

[!h]
\centering\begingroup\fontsize{10}{12}\selectfont

\begin{tabular}[t]{lc}
\toprule
\multicolumn{2}{c}{\textbf{ }} \\

\multicolumn{1}{c}{\textbf{ }} & \multicolumn{1}{c}{\textbf{Life Expectancy Summary}} \\
\cmidrule(l{3pt}r{3pt}){2-2}
Region/Income/Gender & Life Expectancy\\
\midrule
\cellcolor{gray!10}{Global} & \cellcolor{gray!10}{72.13}\\
Male & 69.71\\
\cellcolor{gray!10}{Female} & \cellcolor{gray!10}{74.62}\\
Africa & 64.17\\
\cellcolor{gray!10}{Asia} & \cellcolor{gray!10}{73.97}\\
\addlinespace
North America & 75.04\\
\cellcolor{gray!10}{South America} & \cellcolor{gray!10}{75.18}\\
Oceania & 70.17\\
\cellcolor{gray!10}{Europe} & \cellcolor{gray!10}{78.50}\\
lower\_income & 62.35\\
\addlinespace
\cellcolor{gray!10}{lower\_middle} & \cellcolor{gray!10}{68.40}\\
upper\_middle & 73.38\\
\cellcolor{gray!10}{high\_income} & \cellcolor{gray!10}{79.38}\\
\bottomrule
\end{tabular}
\endgroup{}

This table shows the cleaned data of life expectancy at different
predictor. We could visual that high income has the highest life
expectancy of 79.8, compared to lower income has the least life
expectancy of 62.35. Among all the region, it's clear that Africa has
the least 64.17, while Europe has the highest 78.50 years old. Female
has slightly higher life expectancy than male.

\end{table}%

@@

Figure~\ref{fig-expectancy} visualizes the distribution of life
expectancy from 2015 to 2020 as percentages. The histogram visualizes
the distribution of life expectancy grouped into 5-year ranges,
expressed as percentages. Most of the data lies between the ranges of
66--81 years, with the largest percentage (24.7\%) in the 76--81 range.
This suggests that a significant portion of individuals have life
expectancy within this range. The data also shows smaller percentages at
the lower (46--56 years) and higher ends (81--86 years). Additionally, a
small percentage of missing (NA) values may highlight areas for data
quality. Even we remove the NA while cleaning, the data of NA still
exists for not belongs to any of these ranges.

@@

\caption{\label{fig-expectancy}This histogram shows the distribution of
the percentage of life expectancy for all years. Among all the life
expectancy ranges, 76-81 has the largest percenage of 24.7\%, while the
46-51 has the 0.54\%. Life expectancy shows a growing trend with the
increasing of age and drop sharply comes to the 81-86 range.}

@@

\begin{table}
\centering
\caption{Summary Statistics of Life Expectancy}
\centering
\fontsize{14}{16}\selectfont
\begin{tabular}[t]{>{}c|>{}c|>{}c|>{}c|>{}c|>{}c}
\hline
\multicolumn{6}{c}{ } \\

\cellcolor{lightgray}{\textbf{Mean}} & \cellcolor{lightgray}{\textbf{Median}} & \cellcolor{lightgray}{\textbf{Max}} & \cellcolor{lightgray}{\textbf{Standard Deviation}} & \cellcolor{lightgray}{\textbf{Variance}} & \cellcolor{lightgray}{\textbf{N}}\\
\hline
\cellcolor{darkblue}{\textcolor{white}{\textbf{72.2}}} & \textcolor{black}{73.1} & \textcolor{black}{87.4} & \textcolor{black}{7.8} & \textcolor{black}{60.1} & \textcolor{black}{3312}\\
\hline
\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note:} This table summarizes the key statistics of life expectancy data.}\\
\end{tabular}
\end{table}

@@

\begin{align} 
y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \text{(1)} \\
\mu_i &= \alpha + \beta_1 \text{Region}_i + \beta_2 \text{Gender}_i + \beta_3 \text{Income_Group}_i \\text{(2)} \\
\alpha &\sim \text{Normal}(0, 2.5) \text{(3)}\\
\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 2.5) \text{(4)}\\
\sigma &\sim \text{Exponential}(1) \text{(5)} \\
\end{align}

@@

RMSE measures the square root of the average squared differences between
the predicted and observed values. In the context of this model, RMSE
quantifies how closely the predicted life expectancy values align with
the actual observed values. Lower RMSE values indicate better model
performance, suggesting that the model's predictions are close to the
true values. Table~\ref{tbl-modelpredict} gives out the RMSE of both
testing data and training data. The generalizability is checked by
comparing rmse\_test and rmse\_train. Seeing the test RMSE is slightly
lower than the training RMSE, the model generalizes well.

@@

Extended versions of the table can be found in
Table~\ref{tbl-testpredicted}.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Split the dataset into training and testing sets (80\% train, 20\% test)}
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)  }\CommentTok{\# Setting seed for reproducibility}
\NormalTok{train\_index }\OtherTok{\textless{}{-}} \FunctionTok{createDataPartition}\NormalTok{(leab}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Life Expectancy}\StringTok{\textasciigrave{}}\NormalTok{, }\AttributeTok{p =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{list =} \ConstantTok{FALSE}\NormalTok{)}

\NormalTok{train\_data }\OtherTok{\textless{}{-}}\NormalTok{ leab[train\_index, ]}
\NormalTok{test\_data }\OtherTok{\textless{}{-}}\NormalTok{ leab[}\SpecialCharTok{{-}}\NormalTok{train\_index, ]}

\CommentTok{\# Predict life expectancy using the test data}
\NormalTok{predictions }\OtherTok{\textless{}{-}} \FunctionTok{predict}\NormalTok{(model\_developed, }\AttributeTok{newdata =}\NormalTok{ test\_data)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tbl-modelpredict}Summary of the life expectancy model,
which includes gender, region and income group. The table presents the
model RSME and out-of sample testing.}

\centering
\caption{RMSE Comparison for Test and Training Data}
\centering
\fontsize{14}{16}\selectfont
\begin{tabular}[t]{>{}c|>{}c}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{1}{c}{Root Mean Squared Error (RMSE)} \\
\cline{2-2}
Dataset & RMSE\\
\hline
\cellcolor{steelblue}{\textcolor{white}{\textbf{Test Data}}} & \textcolor{black}{1.15}\\
\hline
\cellcolor{steelblue}{\textcolor{white}{\textbf{Training Data}}} & \textcolor{black}{1.17}\\
\hline
\end{tabular}

\end{table}%

@@

\subsection{Data results analysis}\label{data-results-analysis}

According to the Table~\ref{tbl-sum_sta}, we could tell that

@@

Our results are summarized in Table~\ref{tbl-model}. We are primarily
interest in the general life expectancy regarding to the related
predictors. The multiple linear model provides us with the estimates for
the intercept and coefficients for the predictors which are male,
female, both genders, lower income, lower-middle, upper-middle, high
income, Asia, Europe, Africa, Oceania, North America and South America.
The intercept represents the estimate of region-standard life expectancy
when all the predictors are zero. The coefficients represent the
additional life expectancy associated with each predictor. The model
results will display the estimates- posterior means or medians for each
coefficient including the intercept, uncertainty measures- credible
intervals. The output values of each predictor is the regression
coefficient, meaning how much the outcome is expected to increase or
decrease with one unit increase in the life expectancy (per year) of
that predictor, holding all else constant. The value in the brackets
represent the Median Absolute Deviation of the posterior distributions
of the coefficients. It conveys the dispersion around the median of each
coefficients' posterior distribution, exhibiting how spread the
distributions are.

Num.Obs represents the number of observations made in the model. R2 is
the R-squared value which is the proportion of variance in the dependent
variable that can be explained bu the independent variable. The R2 adj
is the adjusted R squared which accounts for the number of predictors
used. Log.lik is the log-likelihood which gives us an idea of the
likelihood of the data, higher is the better, but this is typically used
for comparison between the models. ELPD and ELPD s.e. explains the log
predictive density and its standard error. The ELPD measures the sum of
the log predictive densities for each observation, used for model
comparison. LOOIC is an acronym for leave-one-out information criterion
in which a lower value indicates a model with better out-of-sample
predictive performance. WAIC stands for Watanabe-Akaike information
criterion which is another measure of good fit; lower values are better
fit. RMSE is the room mean squared error measuring the models's
predictive performance where lower values means more accurate predicts.

\begin{table}

\caption{\label{tbl-model}Summary of the life expectancy model, which
includes gender, region and income group. The table presents the model
RSME and out-of sample testing.}

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]},
column{1}={halign=l,},
column{2}={halign=c,},
hline{390}={1,2}{solid, 0.05em, black},
}                     %% tabularray inner close
\toprule
& Gaussian(Normal) \\ \midrule %% TinyTableHeader
(Intercept)                                                 & \num{79.53}     \\
& (\num{43.50})   \\
RegionAsia                                                  & \num{-6.22}     \\
& (\num{21.20})   \\
RegionEurope                                                & \num{-8.39}     \\
& (\num{45.65})   \\
RegionNorth America                                         & \num{-5.48}     \\
& (\num{50.68})   \\
RegionOceania                                               & \num{-8.43}     \\
& (\num{80.66})   \\
RegionSouth America                                         & \num{21.91}     \\
& (\num{55.21})   \\
CountryAlbania                                              & \num{0.68}      \\
& (\num{28.99})   \\
CountryAlgeria                                              & \num{9.41}      \\
& (\num{47.74})   \\
CountryAngola                                               & \num{-4.60}     \\
& (\num{47.88})   \\
CountryAntigua and Barbuda                                  & \num{2.12}      \\
& (\num{31.15})   \\
CountryArgentina                                            & \num{-28.26}    \\
& (\num{65.45})   \\
CountryArmenia                                              & \num{-3.20}     \\
& (\num{29.08})   \\
CountryAustralia                                            & \num{17.28}     \\
& (\num{64.59})   \\
CountryAustria                                              & \num{7.63}      \\
& (\num{26.97})   \\
CountryAzerbaijan                                           & \num{-2.97}     \\
& (\num{29.29})   \\
CountryBahamas                                              & \num{-1.15}     \\
& (\num{31.29})   \\
CountryBahrain                                              & \num{3.35}      \\
& (\num{36.83})   \\
CountryBangladesh                                           & \num{4.23}      \\
& (\num{54.21})   \\
CountryBarbados                                             & \num{2.55}      \\
& (\num{30.97})   \\
CountryBelarus                                              & \num{-3.11}     \\
& (\num{29.12})   \\
CountryBelgium                                              & \num{7.36}      \\
& (\num{26.87})   \\
CountryBelize                                               & \num{0.25}      \\
& (\num{30.40})   \\
CountryBenin                                                & \num{-3.17}     \\
& (\num{48.20})   \\
CountryBhutan                                               & \num{4.36}      \\
& (\num{54.23})   \\
CountryBolivia (Plurinational State of)                     & \num{-24.08}    \\
& (\num{76.01})   \\
CountryBosnia and Herzegovina                               & \num{-0.20}     \\
& (\num{29.18})   \\
CountryBotswana                                             & \num{-19.85}    \\
& (\num{51.26})   \\
CountryBrazil                                               & \num{-30.04}    \\
& (\num{65.42})   \\
CountryBrunei Darussalam                                    & \num{4.00}      \\
& (\num{36.91})   \\
CountryBulgaria                                             & \num{-2.45}     \\
& (\num{29.09})   \\
CountryBurkina Faso                                         & \num{-5.08}     \\
& (\num{21.33})   \\
CountryBurundi                                              & \num{-3.23}     \\
& (\num{21.40})   \\
CountryCabo Verde                                           & \num{7.65}      \\
& (\num{47.94})   \\
CountryCambodia                                             & \num{-0.02}     \\
& (\num{54.13})   \\
CountryCameroon                                             & \num{-5.86}     \\
& (\num{48.02})   \\
CountryCanada                                               & \num{7.86}      \\
& (\num{30.96})   \\
CountryCentral African Republic                             & \num{-14.92}    \\
& (\num{21.25})   \\
CountryChad                                                 & \num{-8.32}     \\
& (\num{21.18})   \\
CountryChile                                                & \num{-24.65}    \\
& (\num{56.84})   \\
CountryChina                                                & \num{-4.35}     \\
& (\num{51.31})   \\
CountryColombia                                             & \num{-27.30}    \\
& (\num{65.38})   \\
CountryComoros                                              & \num{1.26}      \\
& (\num{48.11})   \\
CountryCongo                                                & \num{-3.93}     \\
& (\num{48.00})   \\
CountryCosta Rica                                           & \num{5.85}      \\
& (\num{30.49})   \\
CountryCote d'Ivoire                                        & \num{-4.15}     \\
& (\num{48.20})   \\
CountryCroatia                                              & \num{4.47}      \\
& (\num{26.98})   \\
CountryCuba                                                 & \num{3.41}      \\
& (\num{30.53})   \\
CountryCyprus                                               & \num{8.31}      \\
& (\num{26.83})   \\
CountryCzechia                                              & \num{5.01}      \\
& (\num{27.04})   \\
CountryDemocratic People's Republic of Korea                & \num{11.23}     \\
& (\num{0.48})    \\
CountryDemocratic Republic of the Congo                     & \num{-5.91}     \\
& (\num{21.28})   \\
CountryDenmark                                              & \num{7.40}      \\
& (\num{26.95})   \\
CountryDjibouti                                             & \num{-1.98}     \\
& (\num{47.97})   \\
CountryDominican Republic                                   & \num{-0.78}     \\
& (\num{30.48})   \\
CountryEcuador                                              & \num{-28.26}    \\
& (\num{65.51})   \\
CountryEgypt                                                & \num{4.21}      \\
& (\num{47.84})   \\
CountryEl Salvador                                          & \num{-0.99}     \\
& (\num{30.48})   \\
CountryEquatorial Guinea                                    & \num{-22.60}    \\
& (\num{51.41})   \\
CountryEritrea                                              & \num{-3.74}     \\
& (\num{21.28})   \\
CountryEstonia                                              & \num{4.46}      \\
& (\num{26.91})   \\
CountryEswatini                                             & \num{-12.28}    \\
& (\num{48.03})   \\
CountryEthiopia                                             & \num{1.13}      \\
& (\num{21.26})   \\
CountryFiji                                                 & \num{-0.68}     \\
& (\num{71.02})   \\
CountryFinland                                              & \num{7.61}      \\
& (\num{27.08})   \\
CountryFrance                                               & \num{8.48}      \\
& (\num{26.98})   \\
CountryGabon                                                & \num{-19.19}    \\
& (\num{51.46})   \\
CountryGambia                                               & \num{-2.56}     \\
& (\num{21.32})   \\
CountryGeorgia                                              & \num{-3.87}     \\
& (\num{29.20})   \\
CountryGermany                                              & \num{7.02}      \\
& (\num{27.00})   \\
CountryGhana                                                & \num{-1.35}     \\
& (\num{47.86})   \\
CountryGreece                                               & \num{7.16}      \\
& (\num{26.98})   \\
CountryGrenada                                              & \num{-1.25}     \\
& (\num{30.43})   \\
CountryGuatemala                                            & \num{-2.17}     \\
& (\num{30.39})   \\
CountryGuinea                                               & \num{-6.20}     \\
& (\num{47.88})   \\
CountryGuinea-Bissau                                        & \num{-8.80}     \\
& (\num{21.23})   \\
CountryGuyana                                               & \num{-37.07}    \\
& (\num{56.78})   \\
CountryHaiti                                                & \num{-1.41}     \\
& (\num{33.25})   \\
CountryHonduras                                             & \num{6.26}      \\
& (\num{33.17})   \\
CountryHungary                                              & \num{2.27}      \\
& (\num{27.02})   \\
CountryIceland                                              & \num{8.69}      \\
& (\num{26.93})   \\
CountryIndia                                                & \num{1.11}      \\
& (\num{54.41})   \\
CountryIndonesia                                            & \num{-10.63}    \\
& (\num{51.36})   \\
CountryIran (Islamic Republic of)                           & \num{7.86}      \\
& (\num{54.06})   \\
CountryIraq                                                 & \num{-9.81}     \\
& (\num{51.25})   \\
CountryIreland                                              & \num{8.03}      \\
& (\num{26.93})   \\
CountryIsrael                                               & \num{9.91}      \\
& (\num{36.89})   \\
CountryItaly                                                & \num{8.81}      \\
& (\num{26.91})   \\
CountryJamaica                                              & \num{-1.99}     \\
& (\num{30.43})   \\
CountryJapan                                                & \num{11.94}     \\
& (\num{36.88})   \\
CountryJordan                                               & \num{9.67}      \\
& (\num{54.24})   \\
CountryKazakhstan                                           & \num{-4.71}     \\
& (\num{29.26})   \\
CountryKenya                                                & \num{-0.86}     \\
& (\num{47.87})   \\
CountryKiribati                                             & \num{4.08}      \\
& (\num{61.70})   \\
CountryKuwait                                               & \num{9.87}      \\
& (\num{36.84})   \\
CountryKyrgyzstan                                           & \num{3.47}      \\
& (\num{54.41})   \\
CountryLao People's Democratic Republic                     & \num{-1.48}     \\
& (\num{54.13})   \\
CountryLatvia                                               & \num{1.45}      \\
& (\num{26.95})   \\
CountryLebanon                                              & \num{9.14}      \\
& (\num{54.11})   \\
CountryLesotho                                              & \num{-15.82}    \\
& (\num{48.08})   \\
CountryLiberia                                              & \num{-4.50}     \\
& (\num{21.35})   \\
CountryLibya                                                & \num{-10.87}    \\
& (\num{51.31})   \\
CountryLithuania                                            & \num{1.52}      \\
& (\num{27.02})   \\
CountryLuxembourg                                           & \num{9.05}      \\
& (\num{26.98})   \\
CountryMadagascar                                           & \num{-3.54}     \\
& (\num{21.21})   \\
CountryMalawi                                               & \num{-4.38}     \\
& (\num{21.25})   \\
CountryMalaysia                                             & \num{-6.51}     \\
& (\num{51.20})   \\
CountryMaldives                                             & \num{-4.14}     \\
& (\num{51.20})   \\
CountryMali                                                 & \num{-6.00}     \\
& (\num{21.21})   \\
CountryMalta                                                & \num{8.28}      \\
& (\num{26.88})   \\
CountryMauritania                                           & \num{2.98}      \\
& (\num{47.95})   \\
CountryMauritius                                            & \num{-9.94}     \\
& (\num{51.30})   \\
CountryMexico                                               & \num{0.67}      \\
& (\num{30.33})   \\
CountryMicronesia (Federated States of)                     & \num{8.09}      \\
& (\num{61.64})   \\
CountryMongolia                                             & \num{1.06}      \\
& (\num{54.16})   \\
CountryMontenegro                                           & \num{-0.28}     \\
& (\num{29.22})   \\
CountryMorocco                                              & \num{6.69}      \\
& (\num{48.03})   \\
CountryMozambique                                           & \num{-9.56}     \\
& (\num{21.26})   \\
CountryMyanmar                                              & \num{-0.94}     \\
& (\num{54.36})   \\
CountryNamibia                                              & \num{-21.00}    \\
& (\num{51.42})   \\
CountryNepal                                                & \num{1.41}      \\
& (\num{54.14})   \\
CountryNetherlands (Kingdom of the)                         & \num{8.02}      \\
& (\num{27.04})   \\
CountryNew Zealand                                          & \num{16.32}     \\
& (\num{64.57})   \\
CountryNicaragua                                            & \num{13.32}     \\
& (\num{33.40})   \\
CountryNiger                                                & \num{-6.88}     \\
& (\num{21.20})   \\
CountryNigeria                                              & \num{-4.28}     \\
& (\num{48.05})   \\
CountryNorth Macedonia                                      & \num{-1.40}     \\
& (\num{29.34})   \\
CountryNorway                                               & \num{8.78}      \\
& (\num{26.93})   \\
CountryOman                                                 & \num{2.38}      \\
& (\num{36.87})   \\
CountryPakistan                                             & \num{-3.13}     \\
& (\num{54.28})   \\
CountryPanama                                               & \num{4.48}      \\
& (\num{31.13})   \\
CountryPapua New Guinea                                     & \num{8.94}      \\
& (\num{61.59})   \\
CountryParaguay                                             & \num{-29.48}    \\
& (\num{65.36})   \\
CountryPeru                                                 & \num{-26.42}    \\
& (\num{65.46})   \\
CountryPhilippines                                          & \num{0.30}      \\
& (\num{54.15})   \\
CountryPoland                                               & \num{3.67}      \\
& (\num{27.01})   \\
CountryPortugal                                             & \num{7.36}      \\
& (\num{27.07})   \\
CountryPuerto Rico                                          & \num{6.28}      \\
& (\num{31.19})   \\
CountryQatar                                                & \num{5.93}      \\
& (\num{36.80})   \\
CountryRepublic of Korea                                    & \num{10.61}     \\
& (\num{36.81})   \\
CountryRepublic of Moldova                                  & \num{-4.72}     \\
& (\num{29.13})   \\
CountryRomania                                              & \num{1.39}      \\
& (\num{26.96})   \\
CountryRussian Federation                                   & \num{-9.31}     \\
& (\num{51.36})   \\
CountryRwanda                                               & \num{0.44}      \\
& (\num{21.29})   \\
CountrySaint Lucia                                          & \num{1.72}      \\
& (\num{30.45})   \\
CountrySaint Vincent and the Grenadines                     & \num{-1.25}     \\
& (\num{30.38})   \\
CountrySamoa                                                & \num{12.64}     \\
& (\num{61.59})   \\
CountrySao Tome and Principe                                & \num{4.58}      \\
& (\num{47.96})   \\
CountrySaudi Arabia                                         & \num{4.35}      \\
& (\num{36.87})   \\
CountrySenegal                                              & \num{1.47}      \\
& (\num{48.01})   \\
CountrySerbia                                               & \num{-1.59}     \\
& (\num{29.20})   \\
CountrySeychelles                                           & \num{-5.53}     \\
& (\num{43.56})   \\
CountrySierra Leone                                         & \num{-7.75}     \\
& (\num{21.34})   \\
CountrySingapore                                            & \num{10.98}     \\
& (\num{36.89})   \\
CountrySlovakia                                             & \num{3.40}      \\
& (\num{27.00})   \\
CountrySlovenia                                             & \num{7.13}      \\
& (\num{27.00})   \\
CountrySolomon Islands                                      & \num{7.87}      \\
& (\num{61.68})   \\
CountrySomalia                                              & \num{-12.52}    \\
& (\num{21.30})   \\
CountrySouth Africa                                         & \num{-19.37}    \\
& (\num{51.43})   \\
CountrySouth Sudan                                          & \num{-8.01}     \\
& (\num{21.29})   \\
CountrySpain                                                & \num{8.85}      \\
& (\num{27.13})   \\
CountrySri Lanka                                            & \num{7.99}      \\
& (\num{54.25})   \\
CountrySudan                                                & \num{1.81}      \\
& (\num{21.31})   \\
CountrySuriname                                             & \num{-31.76}    \\
& (\num{65.41})   \\
CountrySweden                                               & \num{8.42}      \\
& (\num{26.97})   \\
CountrySwitzerland                                          & \num{9.33}      \\
& (\num{27.01})   \\
CountrySyrian Arab Republic                                 & \num{3.97}      \\
& (\num{0.40})    \\
CountryTajikistan                                           & \num{3.09}      \\
& (\num{53.97})   \\
CountryThailand                                             & \num{-4.50}     \\
& (\num{51.28})   \\
CountryTimor-Leste                                          & \num{-0.90}     \\
& (\num{54.22})   \\
CountryTogo                                                 & \num{-4.19}     \\
& (\num{21.21})   \\
CountryTonga                                                & \num{4.42}      \\
& (\num{71.06})   \\
CountryTrinidad and Tobago                                  & \num{0.20}      \\
& (\num{31.16})   \\
CountryTunisia                                              & \num{10.40}     \\
& (\num{47.95})   \\
CountryTürkiye                                              & \num{-4.47}     \\
& (\num{51.31})   \\
CountryTurkmenistan                                         & \num{-12.58}    \\
& (\num{51.24})   \\
CountryUganda                                               & \num{-1.74}     \\
& (\num{21.23})   \\
CountryUkraine                                              & \num{6.68}      \\
& (\num{36.36})   \\
CountryUnited Arab Emirates                                 & \num{8.68}      \\
& (\num{36.79})   \\
CountryUnited Kingdom of Great Britain and Northern Ireland & \num{7.08}      \\
& (\num{27.10})   \\
CountryUnited Republic of Tanzania                          & \num{-0.45}     \\
& (\num{47.88})   \\
CountryUnited States of America                             & \num{4.57}      \\
& (\num{31.22})   \\
CountryUruguay                                              & \num{-27.80}    \\
& (\num{56.83})   \\
CountryUzbekistan                                           & \num{1.65}      \\
& (\num{54.36})   \\
CountryVanuatu                                              & \num{9.66}      \\
& (\num{61.72})   \\
CountryVenezuela (Bolivarian Republic of)                   & \num{-31.90}    \\
& (\num{65.65})   \\
CountryViet Nam                                             & \num{3.94}      \\
& (\num{53.92})   \\
CountryYemen                                                & \num{6.61}      \\
& (\num{0.40})    \\
CountryZambia                                               & \num{-5.46}     \\
& (\num{47.98})   \\
CountryZimbabwe                                             & \num{-8.25}     \\
& (\num{48.08})   \\
Income\_Grouplower\_income                                & \num{-12.06}    \\
& (\num{36.90})   \\
Income\_Grouplower\_middle                                & \num{-4.04}     \\
& (\num{23.94})   \\
Income\_Groupupper\_middle                                & \num{3.40}      \\
& (\num{20.47})   \\
GenderFemale                                                & \num{2.50}      \\
& (\num{0.05})    \\
GenderMale                                                  & \num{-2.42}     \\
& (\num{0.05})    \\
Num.Obs.                                                    & \num{3312}      \\
R2                                                          & \num{0.976}     \\
R2 Adj.                                                     & \num{0.975}     \\
Log.Lik.                                                    & \num{-5231.038} \\
ELPD                                                        & \num{-5409.7}   \\
ELPD s.e.                                                   & \num{94.5}      \\
LOOIC                                                       & \num{10819.4}   \\
LOOIC s.e.                                                  & \num{189.0}     \\
WAIC                                                        & \num{10816.6}   \\
